---
title: "Installation"
author: "Michael Rustler"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Installation}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

# 1 Pre-required software


- [R (>= 3.3.1](https://cloud.r-project.org/): for the development of the R 
package **kwb.qmra** R 3.3.1 was used. However, also later R releases 
(e.g. 3.4) should be working.  

- [Pandoc](http://pandoc.org/installing.html): is required to convert the reports 
from plain text format (markdown) into the different formats (docx, html, pdf). 

- [Miktex](https://miktex.org/download): needs to be installed in case that **pdf** reports 
should be created.


For the advanced user it is further recommended to install the latest version of 
the integrated development environment (IDE) [RStudio Desktop "open source licence"](https://www.rstudio.com/products/rstudio/download2/#download). 


# 2 R Packages

Once all [pre-required software](#pre-required-software) is installed the R 
package installation workflow as described below can be started.


## 2.1 devtools 

The R package `devtools` is required for downloading and installing the R package 
`kwb.qmra` from Github. Installation is done by executing the following 
lines of code in R or RStudio (from now on written as R(Studio)):

```{r eval = FALSE}
if (!require("devtools")) {
  install.packages("devtools", repos = "https://cloud.r-project.org")
}
```

## 2.2 kwb.qmra

Subsequently the R package `kwb.qmra` can be installed in R with the following code:

```{r eval = FALSE}
if(!require("devtools")) { install.packages("devtools") }
devtools::install_github(repo = "KWB-R/kwb.qmra", 
                         build_vignettes = TRUE,
                         dependencies = TRUE)
```

