---
title: "WWTP Old Ford: public irrigation scenario"
author: "Michael Rustler"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Technical workflow: usage}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r echo = FALSE}
is_travis <- identical(Sys.getenv("TRAVIS"), "true")
knitr::opts_chunk$set(eval = is_travis)
```


How to work with the `kwb.qmra` package in R(Studio) is described in the following chapters

Once the R package is installed it can be loaded with the following command in 
R(Studio):

```{r}
library(kwb.qmra)
```


# 1 Input data 

## 1.1 Download 'Old Ford' configuration 

The folder with the csv configuration files for the Old Ford use case are  
located here and can be downloaded with the following command from [ZENODO](https://doi.org/10.5281/zenodo.159527): 

```{r}
temp <- tempdir()
url <- "https://zenodo.org/record/159527/files/QMRA_OldFord.zip"
t_path <- file.path(temp, basename(url))
download.file(url, dest= t_path, mode="wb") 
unzip(t_path, exdir = temp)

scenarios_dir <- file.path(temp, "scenarios")

cat(sprintf("### Available scenarios:\n%s",
            paste(dir(scenarios_dir), collapse = "\n")))
```

In total there are three different `scenarios` available. To the select the first 
one (`r dir(scenarios_dir)[2]`), you need to run the following command:

```{r}
#### DEFINE DIRECTORY ################
confDir <- dir(scenarios_dir,full.names = TRUE)[2]
confDir
```


## 1.2 Import configuration into R

All csv files with the input data for the hypothetical u `dummy` (as shown above) are 
imported into R with the following function:

```{r, message = FALSE, warnings = FALSE }
#### LOAD ############################
config <- config_read(confDir) 
```

# 2 Check input data 

The QMRA will be performed - in case the user does not modify them in R - based on the 
imported input data, which are defined in the configuration folder. 

In case of the dummy configuration, a Monte carlo simulation (n = 10) for 365 exposure events per year for three pathogens and the following input parameters will be performed:


```{r echo = FALSE, message = FALSE, warnings = FALSE }
simulated <- config$inflow[config$inflow$simulate == 1, 1:3]
knitr::kable(simulated,caption = "Simulated pathogens for QMRA (defined in: 'inflow.csv' with 
             simulated = 1):")

knitr::kable(config$inflow[config$inflow$PathogenName %in% simulated$PathogenName,
 c("PathogenID","PathogenName", "PathogenGroup", "type", "min", "max", 
   "ReferenceName","ReferenceLink")], 
 caption = "Inflow concentrations (defined in: 'inflow.csv') for pathogens used for QMRA:")

knitr::kable(config$treatment$schemes,
 caption = "Treatment schemes (defined in: 'treatment_schemes.csv') used for QMRA:")

knitr::kable(config$treatment$processes[config$treatment$processes$TreatmentID %in% config$treatment$schemes$TreatmentID,
c("TreatmentID","TreatmentName", "TreatmentGroup", "PathogenGroup", "type", "min", "max",
  "ReferenceName","ReferenceLink")], 
 caption = "Treatment processes (defined in: 'treatment_proecesses.csv') and assumed log-reductions used for QMRA (from [DEMOWARE, 2015](http://http://demoware.eu/en/results/deliverables/deliverable-d3-1-appropiate-and-user-friendly-methodologies-for-ra_lca_wfp.pdf#page=18)):")


exposure <- list(number_of_repeatings = as.numeric(config$exposure[config$exposure$name == "number_of_repeatings","value"]),
                 number_of_exposures =  as.numeric(config$exposure[config$exposure$name == "number_of_exposures","value"]),
                 volume_perEvent = config$exposure[config$exposure$name == "volume_perEvent",]
                 )


knitr::kable(exposure$volume_perEvent[,c("name", "type", "value")],
 caption = "Ingested volume per event (defined in: row 3 'volume_perEvent' in 'exposure.csv') (source: own assumption)):")


volume_per_event <- kwb.qmra::create_random_distribution(type = exposure$volume_perEvent$type, 
                                     number_of_repeatings = exposure$number_of_repeatings,
                                     number_of_events = exposure$number_of_exposures, 
                                     value = exposure$volume_perEvent$value, 
                                     min = exposure$volume_perEvent$min, 
                                     max = exposure$volume_perEvent$max, 
                                     mode = exposure$volume_perEvent$mode, 
                                     mean = exposure$volume_perEvent$mean,debug = FALSE)


knitr::kable(config$doseresponse[config$doseresponse$PathogenName %in% simulated$PathogenName,], 
              caption = "Dose-response models (defined in: 'doseresponse.csv') used for QMRA (from [QMRAwiki](http://qmrawiki.canr.msu.edu/index.php/Quantitative_Microbial_Risk_Assessment_(QMRA)_Wiki)):")

knitr::kable(config$health[config$health$PathogenName %in% simulated$PathogenName,], 
              caption = "Health parameters (defined in: 'health.csv') for simulated pathogens (from [WHO, 2011](http://apps.who.int/iris/bitstream/10665/44584/1/9789241548151_eng.pdf#page=132)):")


```

# 4 Run risk calculation

Subsequently the risk calculation can be performed in R(Studio) by executing the 
following code, which uses the `config` that was imported and inspected above:

```{r}
risk <- kwb.qmra::simulate_risk(config)
```

All (input & output) data will be saved in the resulting R object `risk` which an be easily 
inspected by the user, e.g.: 


**Input data**


```{r}
str(risk$input)
```


**Output data**


```{r}
str(risk$output)
```

Thus the user has access to all results.

# 5 Visualise results 

Finally the results of the QMRA can be visualised for each system component as shown 
below:


## 5.1 Inflow
```{r, fig.width = 12, fig.height = 6, fig.cap="Simulated inflow concentrations", warning= FALSE}
kwb.qmra::plot_inflow(risk)
```

## 5.2 Treatment
```{r, fig.width = 12, fig.height = 12, fig.cap="Simulated reductions in the treatment plant", warning= FALSE}
kwb.qmra::plot_reduction(risk)
```

## 5.3 Effluent
```{r, fig.width = 12, fig.height = 18, fig.cap="Simulated effluent concentrations", warning= FALSE}
kwb.qmra::plot_effluent(risk)
```

## 5.4 Exposure 
```{r, fig.width = 12, fig.height = 18, fig.cap="Simulated dose per event", warning= FALSE}
kwb.qmra::plot_event_dose(risk)
```

```{r, fig.width = 12, fig.cap="Simulated ingested volume per event", warning= FALSE}
kwb.qmra::plot_event_volume(risk)
```

## 5.5 Health results 

### 5.5.1 Per event
```{r, fig.width = 12, fig.height = 18, fig.cap="Simulated infection probability per event", warning= FALSE}
kwb.qmra::plot_event_infectionProb(risk)
```

```{r, fig.width = 12, fig.height = 18, fig.cap="Simulated illness probability per event", warning= FALSE}
kwb.qmra::plot_event_illnessProb(risk)
```
```{r, fig.width = 12, fig.height = 18, fig.cap="Simulated DALYs per event", warning= FALSE}
kwb.qmra::plot_event_dalys(risk)
```

### 5.5.2 Total 

```{r, fig.width = 12, fig.height = 9, fig.cap="Simulated total infection probability (for all events)", warning= FALSE}
kwb.qmra::plot_total_infectionProb(risk)
```

```{r, fig.width = 12, fig.height = 9, fig.cap="Simulated total illness probability (for all events", warning= FALSE}
kwb.qmra::plot_total_illnessProb(risk)
```

```{r, fig.width = 12, fig.height = 9, fig.cap="Simulated total DALYs (for all events)", warning= FALSE}
kwb.qmra::plot_total_dalys(risk)
```

In addition tables with summary statistics, e.g. for the **total risk** can be generated easily 
as shown below:

```{r, echo = FALSE}
knitr::kable(risk$output$total[risk$output$total$repeatID==1, ], 
             caption = "Total risk (for first repeat of random generation)")
```

## 6 Export results 


E.g. Write reports for all configurations in a folder e.g. `/scenarios` (here: 
`r scenarios_dir`):

```{r eval = FALSE}
kwb.qmra::report_workflow(confDirs = scenarios_dir)

```

